---
title: "02-exercises"
author: "Christopher Brown"
date: "April 13, 2016"
output: html_document
---

This exercise uses the **Fuel Economy** data set from the **AppliedPredicitiveModeling** package.

Note: The following will set-up your environment for this exercise. If you get an error stating that the packages have not been found, you need to install those packages.


```{r,echo=FALSE}

packs <-  c('AppliedPredictiveModeling', 'ggplot2', 'magrittr', 'dplyr')

for( nm in packs ) { 
  # message(nm)
  if( ! nm  %in% installed.packages()[,1]  ) install.packages(nm)
  library(nm, character.only = TRUE)
}

# Load data set into environment
data(FuelEconomy)
... = NULL  # Needed for aesthetics 

```



## Exercise 1

Hint: See `?cars2010`


- After the **Fuel Economy** data is loaded, combine three data sets into one data set. (Note: The name `dat` is very often used in these situations, `data` is a reserved R word.)  

```{r}
dat <- bind_rows( cars2010, cars2011, cars2012)    # Define 
```


- What is a good "naive guess" of FE? Show your work

```{r}
# For all intents and purposes, the mean can actually me a model itself (just a constant). It can be used
# as an initial way to make sure your model is doing better than the the mean. If it's not, you may have to figure
# out how to get a better model. 
naive_guess <- mean(dat$FE)
```


- plot FE (Fuel Econonomy) vs. EngDisp. Plot the naive guess.

```{r}
qplot(x=dat$EngDispl, y=dat$FE) + geom_hline(yintercept=naive_guess, color="red")
```

- Sample 10 observations from `dat`
- Plot this data. Add a line for the naive_guess. 


```{r}

set.seed(314) 

# Sample #used to learn how to take a sample of the overall data. 
# In a bigger data set, this is important so that we don't have to deal with the entire dataset at once. You may get 100-1000 values
# just to get n undertanding of the data.
samp <- dat %>% dplyr::sample_n(10) 

# Plots 
qplot(y=samp$FE, x=samp$EngDispl) + geom_hline(yintercept = naive_guess, color="red")


```


## Exercise 2:


Write a loss functions for calculating:
- Root Mean Square Error
- Mean Absolute Error
- Median Absolute Error

All functions should accept two arguments: 


```{r}

rmse <- function(y,yhat) {
  ( y - yhat )^2  %>% mean   %>% sqrt 
}

mae <- function(y, yhat) {
  (y - yhat) %>% abs() %>% mean()
}

#not sure what the formula for this is (is it the same as median absolute deviation)
medae <- function(y, yhat) { 
  # ...
}

#using the functions to evaluate loss/performance of naive guess
rmse_naive_guess <- rmse(dat$FE, naive_guess)
mae_naive_guess <- rmse(dat$FE, naive_guess)

```

Use these functions to evaluate the loss/performance of:
- the naive guess
- this is mainly done by getting the rmse and mae. The closer to 0, the better. 
- getting the rmse for two different models is useful since you can use the numbers to compare two models.



## Exercise 3: Linear Model and Model Performance 

- Use `lm` to create a linear model fitting the relationship between FE and EngDispl for the cars2010 data set

```{r}
#Creating a model function using the cars2010 dataset as the training data
fit.2010 <- lm(FE ~ EngDispl, data=cars2010)
```

- Use your functions to evaluate the training error
- Use your model to:
-- predict the FE for 2011. What is the RMSE errors associated with the predictions.
-- predict the FE for 2012. What is the RMSE errors associated with the predictions.

```{r}

#remember to use the newdata parameter for the predict function
yhat.2010 <- predict(fit.2010, newdata=cars2010)  #don't really need to do this, but left as is
yhat.2011 <- predict(fit.2010, newdata=cars2011) #predict values of FE for 2011 cars using the cars2011 data as input (uses EngDispl)
yhat.2012 <- predict(fit.2010, newdata=cars2012) #predict values of FE for 2011 cars using the cars2012 data as input (uses EngDispl)

#Evaluate the training error. This is mainly used to evaluate your model against the actual data.
rmse.2010 <- rmse(cars2010$FE, y.2010) # evaluating the training error (how far off is the training data from the predicted data)

#compare the actual data in cars2011 vs. the predicted values (yhat.2011 or yhat.2012) and this gives you the error
# Ideal is as close to 0 as possible
rmse.2011 <- rmse(cars2011$FE, y.2011) 
rmse.2012 <- rmse(cars2012$FE, y.2012)

#The next thing to do is compare the rmse (model performance) against another candidate model

```


```{r}
# DO NOT EDIT 
rmse.2010 
rmse.2011
rmse.2012
```


## Exercise 4: 

- Model the fuel economy (`FE`) as a function of `EngDispl`, `NumCyl` and `VarValve` using the `cars2011` data set.  
- Provide betas


```{r}
fit.2010 <- lm(FE ~ EngDispl + NumCyl + VarValveTiming, data=cars2011)
betas <- fit.2010$coefficients
```
